Exploring the Design Space of Differentially Private Bayesian Inference under Hellinger Distance

### 2019-01-22 ICML2019/main.tex
update the experiments description

\noindent In the following some of the plots show
mean error as a function of the datasize while one
is a whiskers-plot where the y-axis shows the average
accuracy (or equivalently, the error) of the mechanisms, and the x-axis, instead shows
different balanced priors used. The boxes extend from the lower to the upper quartile values
of the data, with a line at the median. A notch on the box around the
median is also drawn to give a rough guide to the significance of
difference of medians; The whiskers extend from the box to show the
range of the data. A blue box in the plots represents the $\hexpmech$'s behavior-- where the sensitivity is calibrated
w.r.t Hellinger distance-- while the green box next to
it represents the performance of a variation of the basic Laplace
mechanism $\lapmech$, and red one is $\ilapmech$ presented in Section (\ref{sec_mechs}) with the same
settings: that is $\epsilon$, data, prior. The variation
considered performs a postprocessing on the released parameters so
that they are consistent. For instance when the sum of the noised
parameters is greater than $n$ we will truncate them so that they sum
up to $n$.

\paragraph{Increasing data size with balanced datasets}
\label{subsubsec_vs_datasize}

\begin{figure}[ht]
\begin{center}
\centering
\subfigure[Increasing data size with prior $\betad(1,1)$, balanced datasets and parameters $\epsilon = 1.0$]
{ \includegraphics[width=0.35\textwidth]{sampling_2d.eps}
\label{fig_vs_datasize_2d}
}

\subfigure[Increasing data size with $\dirichlet(1,1,1)$ prior distribution, balanced datasets and parameters $\epsilon = 1.0$]
{
  \includegraphics[width=0.35\textwidth]{sampling_3d.eps} 
  \label{fig_vs_datasize_3d}
}
\subfigure[Increasing data size with $\dirichlet(1,1,1,1)$ prior distribution, balanced datasets and parameters $\epsilon = 1.0$]
{
  \includegraphics[width=0.35\textwidth]{sampling_4d.eps} 
  \label{fig_vs_datasize_4d}
}
\end{center}
\end{figure}

In Figures \ref{fig_vs_datasize_2d}, \ref{fig_vs_datasize_3d} and \ref{fig_vs_datasize_4d} we still consider \emph{balanced} data sets
of observations. The results show that when the data size increases, the average errors of
$\hexpmech$, $\lapmech$ and $\ilapmech$ decrease. For small datasets,
i.e with size less $300$ in the case of Beta-Binomial models, the Laplace mechanisms outperform $\hexpmech$.
But for bigger data sets, that is, bigger than $300$, or as in Figure \ref{fig_vs_datasize_2d} where
we considered data sets of the order of 15 thousands elements,
the $\hexpmech$ outperforms the $\lapmech$, and asymptotically approaches the improved Laplace mechanism $\ilapmech$.
Similar experimental tendencies were obtained for the Dirichlet-multinomial model (Figure \ref{fig_vs_datasize_3d} and \ref{fig_vs_datasize_4d}).

@@

\paragraph{Experiments on Real Data Sets in Dirichlet-multinomial Model}
We use three real data sets from the same repository repository\footnote{https://archive.ics.uci.edu/ml/datasets.html}. Each data set contains 1 category variable of 3 dimensions ($|\mathcal{X}| = 3$), which applys our 3 dimension Dirichlet-multinomial model. By setting the prior distribution as $\dirichlet(1,1,1)$, we apply our 5 private inference algorithms on them to derive the underlining distribution of these data. The first data set is the SHARING BIKE data, where $0$ means user use sharing bike at workday and $1$ stands for weekend. The second and third data set the THERAPY data, where $1$ means patient with disease is cured and $1$ means not. The forth data set is the BADGE data, $1$ means people with badge and $0$ means without badge. The size of the four data set are $731, 90, 90$. The accuracy are shown in Figure \ref{fig_real_3d}.
\begin{figure}
\centering
\includegraphics[width=0.35\textwidth]{realdata_3d.eps}
\caption{Accuracy on Real Data Sets, with $\epsilon = 1.0$}
\label{fig_real_3d}
\end{figure}

>>>>

\noindent In the following some of the plots show
mean error as a function of the datasize while one
is a whiskers-plot where the y-axis shows the average
accuracy (or equivalently, the error) of the mechanisms, and the x-axis, instead shows
different balanced priors used. The boxes extend from the lower to the upper quartile values
of the data, with a line at the median. A notch on the box around the
median is also drawn to give a rough guide to the significance of
difference of medians; The whiskers extend from the box to show the
range of the data. 
% A blue box in the plots represents the $\hexpmech$'s behavior-- where the sensitivity is calibrated
% w.r.t Hellinger distance-- while the green box next to
% it represents the performance of a variation of the basic Laplace
% mechanism $\lapmech$, and red one is $\ilapmech$ presented in Section (\ref{sec_mechs}) with the same
% settings: that is $\epsilon$, data, prior. The variation
% considered performs a postprocessing on the released parameters so
% that they are consistent. For instance when the sum of the noised
% parameters is greater than $n$ we will truncate them so that they sum
% up to $n$.

% \paragraph{Increasing data size with balanced datasets}
% \label{subsubsec_vs_datasize}

% \begin{figure}[ht]
% \begin{center}
% \centering
% \subfigure[Increasing data size with prior $\betad(1,1)$, balanced datasets and parameters $\epsilon = 1.0$]
% { \includegraphics[width=0.35\textwidth]{sampling_2d.eps}
% \label{fig_vs_datasize_2d}
% }

% \subfigure[Increasing data size with $\dirichlet{1,1,1}$ prior distribution, balanced datasets and parameters $\epsilon = 1.0$]
% {
%   \includegraphics[width=0.35\textwidth]{sampling_3d.eps} 
%   \label{fig_vs_datasize_3d}
% }
% \subfigure[Increasing data size with $\dirichlet{1,1,1,1}$ prior distribution, balanced datasets and parameters $\epsilon = 1.0$]
% {
%   \includegraphics[width=0.35\textwidth]{sampling_4d.eps} 
%   \label{fig_vs_datasize_4d}
% }
% \end{center}
% \end{figure}

% In Figures \ref{fig_vs_datasize_2d}, \ref{fig_vs_datasize_3d} and \ref{fig_vs_datasize_4d} we still consider \emph{balanced} data sets
% of observations. The results show that when the data size increases, the average errors of
% $\hexpmech$, $\lapmech$ and $\ilapmech$ decrease. For small datasets,
% i.e with size less $300$ in the case of Beta-Binomial models, the Laplace mechanisms outperform $\hexpmech$.
% But for bigger data sets, that is, bigger than $300$, or as in Figure \ref{fig_vs_datasize_2d} where
% we considered data sets of the order of 15 thousands elements,
% the $\hexpmech$ outperforms the $\lapmech$, and asymptotically approaches the improved Laplace mechanism $\ilapmech$.
% Similar experimental tendencies were obtained for the Dirichlet-multinomial model (Figure \ref{fig_vs_datasize_3d} and \ref{fig_vs_datasize_4d}).

@@

\paragraph{Experiments on Real Data Sets in Dirichlet-multinomial Model}
We use three real data sets from the same repository repository\footnote{https://archive.ics.uci.edu/ml/datasets.html}. Each data set contains 1 category variable of 3 dimensions ($|\mathcal{X}| = 3$), which applys our 3 dimension Dirichlet-multinomial model. By setting the prior distribution as $\dirichlet{1,1,1}$, we apply our 5 private inference algorithms on them to derive the underlining distribution of these data. The first data set is the SHARING BIKE data, where $0$ means user use sharing bike at workday and $1$ stands for weekend. The second and third data set the THERAPY data, where $1$ means patient with disease is cured and $1$ means not. The forth data set is the BADGE data, $1$ means people with badge and $0$ means without badge. The size of the four data set are $731, 90, 90$. The accuracy are shown in Figure \ref{fig_real_3d}.
\begin{figure}
\centering
\includegraphics[width=0.35\textwidth]{realdata_3d.eps}
\caption{Accuracy on Real Data Sets, with $\epsilon = 1.0$}
\label{fig_real_3d}
\end{figure}
